\modLP{Identification of} Biological Regulatory Networks from Process Hitting models

### 2014-11-06 parts-asp.tex
add modMF

Cardinality rules turn out to be convenient to enumerate all possible parametrizations by creating multiple answer sets.
For functional purposes, a unique label is assigned to every possible set of resources of a given component.
Thus, we denote $\omega_p$ the set of resources of a given component $a$ labeled by $p$,
and naturally, $K_{a,\omega_p}$ is the related parameter.
%and in the following we note $K_{a,\omega_p}$ the parameter of component $a$ whose set of resources $\omega$ is assigned to the label $p$.
We note that labeling the sets of resources of a component is obviously equivalent to labeling its parameters.
Then, suppose that:
\begin{itemize}
  \item $\paramlabel(a, p)$ states that $p$ is a valid label for a set of resources of component $a$ (and therefore $K_{a,\omega_p}$ is a valid parameter);
  \item $\param(a, p, i)$ states that: $K_{a, \omega_p} = i$;
  \item $\inferedparam(a, p)$ states that the parameter inference of $K_{a, \omega_p}$ was conclusive (\pref{pps:param_K}).
\end{itemize}
It is thereby possible to enumerate the possible values of all parameters for which \pref{pps:param_K} was not conclusive, with the following cardinality rule:
\begin{align*}
  & 1\ \{\ \param(\var{A}, \var{P}, \var{I}) \mid \componentlevels(\var{A}, \var{I})\ \}\ \modMF{1}\ \la \\
  & \qquad\qquad\qquad \paramlabel(\var{A}, \var{P}), \nota \inferedparam(\var{A}, \var{P}).
\end{align*}
Indeed, this rule applies to any possible parameter $\var{P}$ of any component $\var{A}$ ($\paramlabel$) whose value is still unknown ($\nota \inferedparam$),
and states that any expression level $\var{I}$ of this component ($\componentlevels$)
is a candidate value for the parameter ($\param$).
Furthermore, both the lower and upper bounds are $1$,
which forces each enumerated parameter to have exactly one value.
%but no upper bound is specified ($\infty$) for the size of each parameter
%(which is in fact already bounded by the number of possible expression levels of the related component).
%each parameter contains at least $1$ value, as stated by the lower bound, and has no upper bound ($\infty$) but the number of expression levels of its component.
In other worlds, this cardinality rule creates as many answer sets as there are \emph{candidate} parametrizations
so that if $K_{a, \omega_p}$ could not be inferred by \pref{pps:param_K}, then
$K_{a, \omega_p} \in \segm{0}{l_a}$
(thus completely disregarding the notion of admissible parametrizations given in \pref{ssec:admissible-K}).

>>>>

Cardinality rules turn out to be convenient to enumerate all possible parametrizations by creating multiple answer sets.
For functional purposes, a unique label is assigned to every possible set of resources of a given component.
Thus, we denote $\omega_p$ the set of resources of a given component $a$ labeled by $p$,
and naturally, $K_{a,\omega_p}$ is the related parameter.
%and in the following we note $K_{a,\omega_p}$ the parameter of component $a$ whose set of resources $\omega$ is assigned to the label $p$.
We note that labeling the sets of resources of a component is obviously equivalent to labeling its parameters.
Then, suppose that:
\begin{itemize}
  \item $\paramlabel(a, p)$ states that $p$ is a valid label for a set of resources of component $a$ (and therefore $K_{a,\omega_p}$ is a valid parameter);
  \item $\param(a, p, i)$ states that: $K_{a, \omega_p} = i$;
  \item $\inferedparam(a, p)$ states that the parameter inference of $K_{a, \omega_p}$ was conclusive (\pref{pps:param_K}).
\end{itemize}
It is thereby possible to enumerate the possible values of all parameters for which \pref{pps:param_K} was not conclusive, with the following cardinality rule:
\begin{align*}
  & 1\ \{\ \param(\var{A}, \var{P}, \var{I}) \mid \componentlevels(\var{A}, \var{I})\ \}\ \modMF{1}\ \la \\
  & \qquad\qquad\qquad \paramlabel(\var{A}, \var{P}), \nota \inferedparam(\var{A}, \var{P}).
\end{align*}
Indeed, this rule applies to any possible parameter $\var{P}$ of any component $\var{A}$ ($\paramlabel$) whose value is still unknown ($\nota \inferedparam$),
and states that any expression level $\var{I}$ of this component ($\componentlevels$)
is a candidate value for the parameter ($\param$).
\modMF{
Furthermore, both the lower and upper bounds are $1$,
which forces each enumerated parameter to have exactly one value.
}
%but no upper bound is specified ($\infty$) for the size of each parameter
%(which is in fact already bounded by the number of possible expression levels of the related component).
%each parameter contains at least $1$ value, as stated by the lower bound, and has no upper bound ($\infty$) but the number of expression levels of its component.
In other worlds, this cardinality rule creates as many answer sets as there are \emph{candidate} parametrizations
so that if $K_{a, \omega_p}$ could not be inferred by \pref{pps:param_K}, then
\modMF{
$K_{a, \omega_p} \in \segm{0}{l_a}$
}
(thus completely disregarding the notion of admissible parametrizations given in \pref{ssec:admissible-K}).
